The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-05-30 manuscript/5pillars.Rmd
new automated build script

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
author: "Mark Ziemann"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: 5pillars.bib
csl: briefings-in-bioinformatics.csl
---

Mark Ziemann

Deakin University, Geelong, Australia, School of Life and Environmental Sciences.

ORCID: 0000-0002-7688-6974

@@

Although DVCSs assist with code sharing, they are not considered a long-term archiving solution and
might not survive the "ten-year challenge" of code reproducibility @Perkel2020-io.
To achieve that, the code needs to be deposited to a long-term repository.
Zenodo and Figshare repositories are both good options for long-term archiving of software, and the
link to these should be provided in the respective journal article/pre-print.

@@

* Pierre Poulain @pierrepo (elevate to author)

>>>>

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
author: "Mark Ziemann, Samuel S. Minot, Pierre Poulain, Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: 5pillars.bib
csl: briefings-in-bioinformatics.csl
---

Mark Ziemann<sup>1*</sup>, Samuel S. Minot<sup>2</sup>, Pierre Poulain<sup>3</sup>, Anusuiya Bora<sup>1</sup>

1. Deakin University, School of Life and Environmental Sciences, Geelong, Australia.

2. Fred Hutchinson Cancer Center, Seattle, USA.

3. Université Paris Cité, CNRS, Institut Jacques Monod, Paris, France.

@@

Although DVCSs assist with code sharing, they are not considered a long-term archiving solution and
might not survive the "ten-year challenge" of code reproducibility @Perkel2020-io.
To achieve that, the code needs to be deposited to a long-term repository.

[Zenodo](https://zenodo.org/) and [Software Heritage](https://www.softwareheritage.org/) repositories
are both good options for long-term archiving of software, and the
link to these should be provided in the respective journal article/pre-print.

@@
